A self-consistency check for unitary propagation of Hawking quanta

### 2016-10-12 Draft_BH_shells.tex
update bib

Since unitarity is lost to the local geometric uncertainty, what restores information must be the interaction with the local geometry. 
An abstract realization of this information-recovery process is recently demonstrated in \cite{OsuPag16}. 
In order for local geometry to give this information to the Hawking quanta, it must first carry such information.
If was first suggested that superpositions of different classical geometries can store such information \cite{NomVar12}.
In the conventional picture, classical geometries are determined by only a few parameters such as the location and size of the black hole.
Thus the major objection to such picture is that the superpositons of classical geometries do not form a large enough Hilbert space to hold the required information.
Recently, it was realized that there are actually a much larger number of classical geometries differed by their soft hairs \cite{HawPer16}.
A simple counting suggested that the size of Hilbert space seems no longer the problem, so one should persue this line of thoughts even further.

Classically, soft hairs manifest as memory effects that alters the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
Based on this picture, one may try to quantize the soft hairs and build a toy model that involves quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
That would provide a complete picture that the loss of subsystem unitarity is really just entanglement with another subsystem which was originally (and illegitimately, as we argued) assumed as the classical background.

>>>>

Since unitarity is lost to the local geometric uncertainty, what restores information must be the interaction with the local geometry.
More precisely, the particular effect of local geometric uncertainty here is to create extra shifts between parallel null geodesics, which is reminiscent of memory effects or supertraslation\cite{GW_memory,HeLys14,KodPen16}.
This naturally echoes the idea that the soft hairs \cite{HawPer16} encodes the black hole information and returns them to the Hawking radiation via an interaction that is beyond the na\"ive local QFT\cite{OsuPag16}. 
Based on this picture, one may try to quantize the soft hairs and build a toy model that involves quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
That would provide a complete picture that the loss of subsystem unitarity is really just entanglement with another subsystem which was originally (and illegitimately, as we argued) assumed as the classical background.

\acknowledgements

We thank XXX for discussions.
